Asymmetric relationships and their effects on coexistence: Supporting information

### 2023-08-01 paper/SupMat.Rnw
mostly trimming to get under the 5000 word length for the main text

Contributions of ATAs to species coexistence open the possibility that
``ATA specialists'' may exist. For instance, if a strong competitor is present across a
collection of habitat patches on a landscape and the GWR of a weaker competitor is only positive 
in a patch if there are 
ATAs between the temporal fluctuations of two environmental variables in that patch,
then the weaker competitor can only persist in patches for which ATAs are present.
The weaker competitor can therefore perhaps be regarded as an ``ATA specialist'' in the landscape. EC-associations
can boil down to associations between two environmental variables, as was the case
for the lottery model. For the lottery model, $B_i(t)=E_i(t)$ was assumed, and $C_{i \bs i}$ simplified to $E_j(t)/\delta$ (see SI section 
\ref{SIsect:TheoryForLotteryBoth}). Thus, EC-associations parallel associations between the two
environmental variables $E_i(t)$ and $E_j(t)$ for the lottery model, and ATA specialists may exist. 
Mechanisms of coexistence should correspond to
means by which niche differentiation is possible. Thinking about our new mechanism of 
coexistence in terms of possible ATA specialists helps highlight this connection. Likewise,
because we have described ATA exclusion as well as ATA rescue, it is possible to 
imagine a scenario in which a weaker competitor can only exist in habitat patches 
for which ATAs between environmental variables are absent, and is hence a specialist on scenarios with symmetric
tail associations of variables (an ``STA specialist''). Additional 
research will be needed to assess to what degree these possibilities are realized 
in nature.

>>>>

Contributions of ATAs to species coexistence open the possibility that
``ATA specialists'' may exist. For instance, if a strong competitor is present across a
collection of habitat patches on a landscape and the GWR of a weaker competitor is only positive 
in a patch if there are 
ATAs between the temporal fluctuations of two environmental variables in that patch,
then the weaker competitor can only persist in patches for which ATAs are present.
The weaker competitor can therefore perhaps be regarded as an ``ATA specialist'' in the landscape. EC-associations
can boil down to associations between two environmental variables, as was the case
for the lottery model. For the lottery model, $B_i(t)=E_i(t)$ was assumed, and $C_{i \bs i}$ simplified to $E_j(t)/\delta$ (see SI section 
\ref{SIsect:TheoryForLotteryBoth}). Thus, $EC$-associations parallel associations between the two
environmental variables $E_i(t)$ and $E_j(t)$ for the lottery model, and ATA specialists may exist. 
Mechanisms of coexistence should correspond to
means by which niche differentiation is possible. Thinking about our new mechanism of 
coexistence in terms of possible ATA specialists helps highlight this connection. Likewise,
because we have described ATA exclusion as well as ATA rescue, it is possible to 
imagine a scenario in which a weaker competitor can only exist in habitat patches 
for which ATAs between environmental variables are absent, and is hence a specialist on scenarios with symmetric
tail associations of variables (an ``STA specialist''). Additional 
research will be needed to assess to what degree these possibilities are realized 
in nature.
